---
title: "Report"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    fig_width: 6 
    fig_height: 4 
    df_print: paged
    keep_md: true
  pdf_document: default

params:
  d: "C:/Users/Meghana/Desktop/Exploratory Analysis/SampleWithShiny/R/iris.csv"
  freq_param: "None"
  qq_param: "None"
  skew_param: "None"
  violin_param: "None"
  bar_param: "SepalLengthCm"
  target1_param: "SepalLengthCm"
  target2_param: "PetalLengthCm"
  target_factor_param: "Species"
  tsne_param: "Species"
  tsne_perplexity: "30"
  collinearity_param: "PetalLengthCm"
---
<div style="margin-bottom:100px;">

```{r setup, echo = FALSE}
  library(ggplot2)
  library(knitr)
  library(plotly)
  library(Cairo)
knitr::opts_chunk$set(echo = TRUE)
```

<div style="margin-bottom:100px;">
subtitle: <h1><u>Input Dataset</u></h1>
$~$
$~$
```{r, echo = FALSE}
library(knitr)
library(kableExtra)
input_data = read.csv(params$d)
c  = treating_mis_values(input_data)
kable(input_data, caption = "Input Dataset")%>%
  kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover","condensed", "responsive"))%>% scroll_box(height = "400px", width = "100%")
```

$~$
$~$
<div style="margin-bottom:100px;">
<h1><u>Attributes</u></h1>
```{r,echo=FALSE}
library(knitr)
library(kableExtra)
table1 = variable_types(c)
kable(table1)%>%
  kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%")

```

$~$
$~$
<h1><u>Numerical Attributes</u></h1>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
table2 = num_properties_mydata_pdf(c)

kable(table2)%>%
kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%") 

n<-nrow(table2)
str_vec <- vector()
#mean and median Inferences
HTML("<b> Inferences based on Mean and Median</b></br>")
for(i in 1:n)
{
  x<-as.numeric(as.character(table2$Median[i]))
  y<-as.numeric(as.character(table2$Mean[i]))

  if(x < y)
  {
    current_str <- paste("The feature <b>",table2$Column[i]," </b> might have the outliers in the high end of the distribution",sep = "")
  }
  
  else if(x > y)
  {
    current_str <- paste("The feature <b>",table2$Column[i],"</b> might have the outliers in the low end of the distribution",sep="")
  }

  else
  {
    current_str <- paste("The feature  <b>",table2$Column[i],"</b> might not contain the outliers",sep = "")
  }
  str_vec <- c(str_vec, current_str)
}
      HTML(paste(str_vec, collapse = '<br/>'))
      HTML("</br>")
      
      
#SD Inferences      
x<-as.numeric(rownames(table2[which.max(table2$Sd),]))
f<-table2$Column[[x]]
HTML("<b> </br>Inferences based on Standard deviation and Variance</b></br>")
HTML(paste("The feature <b>",f," </b> spread is more.Beware of this feature if it is supposed to be restricted</br>"))

HTML("<b></br>Missing Data</b></br>")
str_vec <- vector()
for(i in 1:n){
 x<-as.numeric(as.character(table2$Num_missing_val[i]))
 
if(x == 0)
{
current_str <- paste("The feature <b>",table2$Column[i]," </b> does not have any missing values",sep = "")
 }

  else if(x > 0)
  {
      #should check if the missing values are dominating or not
      F<-as.character(table2$Column[i])
       ds<-c
      y<-round(0.05*nrow(ds))
      
      if(x<y)
       {
        current_str <- paste("The feature <b>",table2$Column[i],"</b> has missing values.These data points can be omitted from analysis",sep="")
        }
      
      else
      {
       current_str <- paste("The feature <b>",table2$Column[i],"</b> has more missing values.These values should be treated",sep="")
       }
  }
         
  str_vec <- c(str_vec, current_str)
  #print(paste("str_vec =", str_vec))
  }
  HTML(paste(str_vec, collapse = '<br/>'))
  
  HTML("</br")
  HTML("</br>")
  HTML("</br>")
  cat("\n")
#Se Infer  

str_vec <- vector()
HTML("<b></br>Sample Estimates</b></br>")

for(i in 1:n)
  {
    x<-as.numeric(as.character(table2$Se[i]))
    y<-as.numeric(as.character(table2$Mean[i]))
    z<-y/3
  
    if(x>z)#se is high
    {
      current_str <- paste("The sample for the feature <b>", table2$Column[i]," </b> is not a proper represenative of the population",sep = "")
    }
    
    else
    {
      current_str <- paste("The sample for the feature <b>", table2$Column[i]," </b> is  a proper represenative of the population",sep = "")
    }
       
    str_vec <- c(str_vec, current_str)
    #print(paste("str_vec =", str_vec))
    
  }
      HTML(paste(str_vec, collapse = '<br/>'))
      HTML("</br>")

#Skew Inferences
HTML("<b></br>Shape Estimates</b></br>")
      str_vec <- vector()
      for(i in 1:n)
      {
        x<-as.numeric(as.character(table2$skewness[i]))
        y<-round(as.numeric(as.character(table2$kurtosis[i])),1)
        #print(x)
        if(x< -1 || x>1)
        {
          #highly skewed
          if(y>0)#longer tails - excess outliers
          {
            current_str <- paste("The feature <b>",table2$Column[i]," </b>highly deviates from normal distribution.Outliers are suspected",sep = "")
          }
          else if(y<0)#shorter tails
          {
          current_str <- paste("The feature <b>",table2$Column[i]," </b>highly deviates from normal distribution.Also check for any data entry errors",sep = "")
          }
        }
        else if((-1<x && x< -0.5) || (0.5<x && x<1) )
        {
          #moderately skewed
          if(y>0)
          {
            current_str <- paste("The feature <b>",table2$Column[i]," </b>slightly deviates from normal distribution.Outliers are suspected.",sep = "")
          }
          else if(y<0)
          {
          current_str <- paste("The feature <b>",table2$Column[i],"</b> slightly deviates from the normal distribution.Kindly check for the data entry errors",sep="")
          }
        }
         
       else if(-0.5<x && x<0.5)
          {
           if(y==0)
           {
            current_str <- paste("The feature <b>",table2$Column[i],"</b> is symmetric.",sep="")
           }
           else
           {
             current_str <- paste("The feature <b>",table2$Column[i]," </b>is almost symmetric.",sep = "")
           }
          }
        str_vec <- c(str_vec, current_str)
        #print(paste("str_vec =", str_vec))
      }
      HTML(paste(str_vec, collapse = '<br/>'))
   
```

$~$
$~$
<h1><u>Categorical Attributes</u></h1>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(xml2)
table3 = cat_properties_mydata_pdf(c)

kable(table3)%>%
kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%")

n<-nrow(table3)
ds<-c
str_vec <- vector()
HTML(paste("<b> Inferences based on Mode </b></br>"))

        str_vec <- vector()

        for(i in 1:n){
          f<-as.character(table3$Column[i])
           nl<-nlevels(ds[[f]])
           l<-levels(ds[[f]])
           
           s<-paste(l,collapse = ", ")
         
           current_str<-paste("The feature has <b>",nl," </b> levels.And they are <b>
                              ",s,"</b>")
           
           #trying to find the dominating level
           dl <- ds%>%group_by_at(f)%>%summarise(count=n())
           z  <-dl[dl$count==max(dl$count),f]
           r<-paste(z[[f]],collapse = " , ")
           current_str<-paste0(current_str,"</br>The levels <b> ",r," </b> have dominant values </br>")
           str_vec <- c(str_vec, current_str)
          #print(paste("str_vec =", str_vec))
        }
       
        HTML(paste(str_vec, collapse = '<br/>'))

```

$~$
$~$
<h1><u>Histogram Plots</u></h1>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(plotly)
total_len = length(names(Filter(is.numeric, c))) + length(names(Filter(is.logical, c)))
contin_col_names = names(Filter(is.numeric, c))
contin_col_names = c(contin_col_names, names(Filter(is.logical, c)))
contin_cols = which(names(c) %in% contin_col_names)
output_freq = list()

for(i in 1:total_len)
{
  p = contin_cols[i]
  
  if(params$freq_param=="None")
    bp = plot_ly(x = c[[p]], type = "histogram") %>%  layout(xaxis = list(title = names(c)[p], zeroline = FALSE),yaxis = list(title = "Count", zeroline = FALSE))
  
  
  if(params$freq_param!="None")
    bp = plot_ly(c, x = c[[p]], color = ~get(params$freq_param)) %>% add_histogram() %>% layout(xaxis = list(title = names(c)[p]))
  
   output_freq[[length(output_freq) + 1L]] <- bp

}

for(j in 1:length(output_freq)){
  x <- output_freq[[j]]

  if(inherits(x, "character")){
    cat("\n")
    cat(x)
  } else if(inherits(x, "knitr_kable")){
    cat("\n")
    print(x)
  }
  else {
    # print the html piece of the htmlwidgets
    cat("\n")
    cat(htmltools::renderTags(as.widget(x))$html)
  }
}

```

$~$
$~$
<h1><u>QQ Plots</u></h1>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(plotly)
library(ggplot2)
total_len = length(names(Filter(is.numeric, c))) + length(names(Filter(is.logical, c)))
contin_col_names = names(Filter(is.numeric, c))
contin_col_names = c(contin_col_names, names(Filter(is.logical, c)))
contin_cols = which(names(c) %in% contin_col_names)
output_qq = list()
ds = c
for(i in 1:total_len)
{
  p = contin_cols[i]
  z = as.character(params$qq_param)
  
  if(z=="None")
  {
    gg <- ggplot(ds, aes(sample = ds[[p]])) + stat_qq() + stat_qq_line()+ggtitle(label = paste("QQ Plot for", names(ds)[p]))
    bp <- ggplotly(gg)
cat(knit_print(bp))    
    }

  else
  {
    #bp<-ggplot(ds, aes(sample = ds[[p]])) + stat_qq() + stat_qq_line()+ggtitle(label = paste("QQ Plot for", names(ds)[p]))
    bp<-ggqqplot(ds, x =names(ds[p]) ,color = z, ggtheme = theme_pubclean(), title = label("QQ Plot for", names(ds)[p]))
              bp<-ggplotly(bp)
    cat(knit_print(bp))
    
  }
   output_qq[[length(output_qq) + 1L]] <- bp

}

# for(j in 1:length(output_qq)){
#   x <- output_qq[[j]]
#   print(output_qq[[p]])
#   cat("\n")
# }
```

$~$
$~$
<h1><u>Density Plots</u></h1>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(plotly)
library(rmarkdown)
library(shinyWidgets)
library(ggplot2)
library(irlba)
library(plot3D)
library(dplyr)
# total_len = length(names(Filter(is.numeric, c))) + length(names(Filter(is.logical, c)))
# contin_col_names = names(Filter(is.numeric, c))
# contin_col_names = c(contin_col_names, names(Filter(is.logical, c)))
# contin_cols = which(names(c) %in% contin_col_names)
output_skew = list()
print(total_len)
for(i in 1:total_len)
{
  p = contin_cols[i]
  
  if(params$skew_param=="None")
  {
      density = density(c[[p]])
      bp <- plot_ly(x = ~density$x, y = ~density$y, type = 'scatter', mode = 'lines', fill = 'tozeroy') %>% layout(xaxis = list(title = names(c)[p]),yaxis = list(title = 'Density'))
      cat(knit_print(bp))
          }

  if(params$skew_param!="None")
  {
    z = as.character(params$skew_param)
         gg = ggplot(c, aes_string(x = names(c)[p], colour = z)) + geom_density() + geom_rug()
      bp = ggplotly(gg)
      cat(knit_print(bp))
      
  }
  
   output_skew[[length(output_skew) + 1L]] <- bp

}


```


$~$
$~$
<h1><u>Violin Plots</u></h1>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(plotly)

total_len = length(names(Filter(is.numeric, c))) + length(names(Filter(is.logical, c)))
contin_col_names = names(Filter(is.numeric, c))
contin_col_names = c(contin_col_names, names(Filter(is.logical, c)))
contin_cols = which(names(c) %in% contin_col_names)
output_violin = list()

for(i in 1:total_len)
{
  p = contin_cols[i]
  
  if(params$violin_param=="None")
  {

    bp <- plot_ly( y = c[[p]], type = 'violin', box = list(visible = T), meanline = list(visible = T), x0 = names(c)[p]) %>% layout(yaxis = list(title = "", zeroline = F))
    cat(knit_print(bp))
          }

  if(params$violin_param!="None")
  {
    z1 = as.character(params$violin_param)
    fig <- c %>% plot_ly( x = ~get(params$violin_param), y = ~get(names(c)[p]), split = ~get(params$violin_param), type = 'violin', box = list(visible = T),meanline = list(visible = T))
   bp <- fig %>% layout(xaxis = list(title = z1), yaxis = list(title = names(c)[p], zeroline = F))
   cat(knit_print(bp))
      
  }
  
   output_violin[[length(output_violin) + 1L]] <- bp

}


```


$~$
$~$
<h1><u>Bar Plots</u></h1>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning =FALSE}
library(knitr)
 library(plotly)
 library(rmarkdown)
 library(shinyWidgets)
 library(Rtsne)
 library(ggplot2)
 library(irlba)
 library(plot3D)
 library(ggcorrplot)
 library(dplyr)
 output_bar = list()
 z1 = as.character(params$bar_param)
 l = names(Filter(is.factor, c))
 l = c(l, names(Filter(is.character, c)))
 print(params$bar_param)
 for(i in 1:length(l))
 {
   if(params$bar_param=="None")
   {
              df2 = c
              z = l[i]
              no = match(z,names(df2))
              df2 <- df2  %>% group_by_(names(.)[no])
              df2 <- df2 %>% dplyr::summarise(count = n())
              fig <- df2 %>% plot_ly(labels = ~get(l[i]) , values = ~count)
              fig <- fig %>% add_pie(hole = 0.6)
              bp <- fig %>% layout(title = paste0(z),  showlegend = T, xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE), yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
             cat(knit_print(bp))
              
              }
   if(params$bar_param!="None")
   {
     q = as.character(params$bar_param)
     print(q)
     gg = ggplot(c) +  geom_bar(aes_string(x = l[i], fill = factor(c[[z1]])))+xlab(z1)
     bp = ggplotly(gg)
     cat(knit_print(bp))
   }
    output_bar[[length(output_bar) + 1L]] <- bp
 }
 
```



$~$
$~$
<h1><u>Outliers</u></h1>
```{r, echo=FALSE}
outlier_table = outlier_detection_chebesheys(c)
kable(outlier_table)%>%
kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%") 

```

$~$
$~$
<h1><u>Data Distribution</u></h1>
```{r, echo=FALSE}
dist_table = distribution(c)
kable(dist_table)%>%
kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%") 

```


$~$
$~$
<h1><u>Correlation</u></h1>
<h3><u>Correlation Table</u></h3>
```{r, echo=FALSE,  results='asis', fig.keep='all', message = FALSE, warning = FALSE}
corr_tables = correlation(c)
  z = as.data.frame(corr_tables[[1]])
  kable(z)%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%") 
```


$~$
$~$
<h3><u>P-Value Table</u></h3>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
  if(!require(DescTools)){install.packages("Hmisc")}
library("Hmisc")
z = as.data.frame(corr_tables[[2]])
  kable(z)%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%") 
  
      t1<-as.data.frame(corr_tables[1])#corr values
      t2<-as.data.frame(corr_tables[2])#p values
      t11<-as.matrix(t1)
      t22<-as.matrix(t2)
      diag(t11)=NA
      diag(t22)=NA
      t11<-melt(t11,na.rm=TRUE)
      t22<-melt(t22,na.rm=TRUE)
      t11<-distinct(t11,value,.keep_all = TRUE)
      attach(t11)
      t11<-t11[order(-value),]
      rownames(t11)<-NULL
      rownames(t22)<-NULL
      n<-nrow(t11)
      str_vec <- vector()
      for(i in 1:n){

        x<-t11$value[i]
        if(x>0)#considering only positive correlations
        {
          v1<-as.character(t11$Var1[i])
          v2<-as.character(t11$Var2[i])
          dt<-t22[(as.character(t22$Var1)==v1 & as.character(t22$Var2)==v2),]
          if(as.numeric(dt$value)<0.05)
          {
            current_str = paste("The features <b>",v1, "-", v2 ,"</b>have a significant correlation value and can be used for feature selection")
			      }
          str_vec <- c(str_vec, current_str)
        }
      }
cat("\n")
cat("\n")
      HTML(paste(str_vec, collapse = '<br/>'))
  cat("\n")
```


$~$
$~$
$~$
$~$
<h1><u>Correlation Heat Map</u></h1>
```{r, echo=FALSE}
library(rmarkdown)
library(shinyWidgets)
library(Rtsne)
library(ggplot2)
library(irlba)
library(plot3D)
library(ggcorrplot)
library(dplyr)

f = c
bp = correlation_heat_map(f)
print(bp)
```


$~$
$~$
<h1><u>Target Variable Analysis</u></h1>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
x_1 = as.character(params$target1_param) 
y_1 = as.character(params$target2_param)

z = as.character(params$target_factor_param)

if(params$target_factor_param =="None")
{
plot_ly(c,x=~get(params$target1_param),y=~get(params$target2_param),mode="markers",type="scatter")%>%layout(title="Plotly Scatter", xaxis = list(title=x_1), yaxis = list(title=y_1))
}

if(params$target_factor_param!="None")
{
 plot_ly(data = c, x = ~get(params$target1_param), y =~get(params$target2_param), color = ~get(params$target_factor_param), colors = "Set1")%>%layout(title="Plotly Scatter", xaxis = list(title=x_1), yaxis = list(title=y_1)) 
}

```


$~$
$~$
<h1><u>tsne</u></h1>
```{r echo=FALSE, fig.keep='all', message=FALSE, warning=FALSE, results='asis'}
library(knitr)
library(ggplot2)
p = as.integer(params$tsne_perplexity)
x = as.character(params$tsne_param)
df2 = c
str_vec = vector()

      if(x =="")
        return()
      if(x!="")
      {
         data_matrix1 = prepare_data(df2, x)
            if(p<(nrow(data_matrix)-1)/3)
            {
              tsne_output = TSNE(df2, data_matrix1,x, p)
              print(tsne_output[[1]])
             iter_no = tsne_output[[2]]
              current_str = paste0("The stable configuration is achieved at iteration ", iter_no,"</br>")
              
              str_vec = c(str_vec, current_str)
              current_str = paste0("The data points that are closer together can be assumed to have few features in common.As these are the points closer together in higher dimensions.")
              str_vec = c(str_vec, current_str)
              
              }

            else
            {
              max<-(nrow(data_matrix1)-1)/3
              current_str = paste0("Choose a perplexity value between 1 and",max)
              str_vec = c(str_vec, current_str)
            }
            HTML(paste(str_vec, collapse = '<br/>'))
            
      }

```


$~$
$~$
<h1><u>Encoded Matrix</u></h1>
```{r, echo=FALSE}
encoded_matrix = encoding(c)
kable(encoded_matrix, caption = "One-Hot Encoding")%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "300px", width = "100%")

```


$~$
$~$
<h1><u>VIF Values</u></h1>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(rmarkdown)
library(shinyWidgets)
library(Rtsne)
library(ggplot2)
library(irlba)
library(plot3D)
library(ggcorrplot)
library(dplyr)
library(car)
library(ISLR)
library(knitr)
z = as.character(params$collinearity_param)
cat("Selected variable: ",z)
v1 = c
v = v1[, sapply(v1, class) != "factor"]
collinearity_output = detect_multicollinearity(v, z, 6)
z1 = as.data.frame(collinearity_output[[1]])
  kable(z1)%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "200px", width = "100%") 
  
```

$~$
$~$
<h1><u>Drop Variables</u></h1>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(rmarkdown)
library(shinyWidgets)
library(Rtsne)
library(ggplot2)
library(irlba)
library(plot3D)
library(ggcorrplot)
library(dplyr)
library(car)
library(ISLR)
library(knitr)
z = as.character(params$collinearity_param)
v = c
v = v[,-1]
z1 = as.data.frame(collinearity_output[[2]])
  kable(z1)%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "200px", width = "100%") 
  
```


$~$
$~$
<h1><u>PCA Analysis</u></h1>
$~$
$~$
<h3><u>PCA Loading Factor Tables </u></h3>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
pca_output = pca(c)
z1 = pca_output[[1]]
kable(z1)%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "200px", width = "100%") 

```

$~$
$~$
<h3><u>PCA Eigen, Sd Value, Variance Values </u></h3>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
z2 = pca_output[[2]]
kable(z2)%>%kable_styling(fixed_thead = T, bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>% scroll_box(height = "200px", width = "100%") 
```


$~$
$~$
<h3><u>Visualization of Variances of Dimensions</u></h3>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(plotly)
bp = pca_output[[3]]
print(bp)
```

$~$
$~$
<h3><u>Individuals of same profile are on the same side of the plot</u></h3>
```{r, echo=FALSE, results='asis', fig.keep='all', message = FALSE, warning = FALSE}
library(knitr)
library(plotly)
bp = pca_output[[4]]
bp
```

